\documentclass{spie}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}
\usepackage{float}

% Set page size and margins
% Replace `letterpaper' with`a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{bm}
\usepackage{tikz}
\newcommand\tab[1][0.5cm]{\hspace*{#1}}

\setlength{\parindent}{0pt}

\title{Project Proposal: CSC240 Spring2022}
\date{March 14, 2022}
\author{Beilei Guo, Liwei Jiang}


\begin{document}
\maketitle

\section{Dataset Choice}

The proposal is to analyze the dataset: "Cryptocurrency Historical Prices" available via Kaggle.

\section{Team Composition}

Liwei Jiang and Beilei Guo will be working together on this final project. Liwei is an undergraduate student pursuing a B.S. in Computer Science, and Beilei Guo is a part-time student pursuing a M.S. in Data Science.

\section{Goal of the Analysis}

This project aims to employ various techniques to develop a model for predicting the future price and transaction volume. The final way to evaluate the performance of the result is still under discussion.

\section{Planned Technical Approach}

\subsection{Visualization}

The analysis will start from basic visualization to achieve a deeper understanding of the dataset. Results will be displayed in various formats, including frequency table, histogram, color printing essay, and n-gram.

\subsection{Data Preprocessing}

A cursory review of the data reveals some unnecessary columns like the name and symbol. Furthermore, the value of the cryptocurrencies of each date is divided into four detailed values and may require to be processed into one value for further analysis. Although we didn't find any missing index yet, a preprocess is still needed.

\subsection{Model Selection}



\section{Role of Team Members}

Beilei will be responsible for future model selection, optimization, and result evaluation. Liwei will take charge of implementing and modifying the selected mining algorithms. Liwei and Beilei will work together to develop the model and deliver a final presentation in class.

\end{document}